### 2015-04-22 Paper1rev2/paper1rev2.tex
updated for work from home

\subsection*{Torque Calculations}

@@

\tau_{ff}=\hat{M}(q_d)\ddot{q}_d+\hat{G}(q_d,\dot{q}_d)+\hat{E}

@@

where $\tau_P$ is calculated from the arm's dynamics, $\tau_{fb}$ is calculated from the impedance model of Burdet et al.\cite{burdet2006stability}, and $c$ is the scaling parameter to be fit. We calculate $\tau_P$ using measured limb segment lengths, $L_1$ and $L_2$ and self-reported body mass, $m_g$. We converted from these gross measurements to specific parameters using the nominal ratios provided in Table~\ref{tab:parameters},

@@

and integrated numerically as described. This provides a check on the fit value $c$ as an inappropriate value would cause $q_d$ to deviate from reasonable values.

>>>>

\subsection*{Torque Calculations for Intent Extraction}

@@

\tau_{ff}=\hat{M}(q_d)\ddot{q}_d+\hat{G}(q_d,\dot{q}_d)

@@

where $E$ is the measured force on the hand converted to joint torques via the Jacobian, $\tau_P$ is calculated from the arm's dynamics, $\tau_{fb}$ is calculated from the impedance model of Burdet et al.\cite{burdet2006stability}, and $c$ is a scalar constant to be fit. We calculate $\tau_P$ using measured limb segment lengths, $L_1$ and $L_2$ and self-reported body mass, $m_g$. Terms followed by a subscript 1 indicate the upper arm or shoulder joint while terms followed by a subscript 2 indicate the forearm or elbow joint. We converted from these gross measurements to specific parameters using the nominal ratios provided in Table~\ref{tab:parameters},

@@

and integrated numerically as described. By scaling an established model using a force disturbance other than our disturbance of interest, we avoided presuming the intent trajectory we hoped to recover.
